\chapter{Literature Review}

\section{Introduction}

This chapter reviews the existing literature relevant to your research topic. It should demonstrate your understanding of the field and position your work within the broader academic context.

\section{Theoretical Framework}

Describe the theoretical foundations that underpin your research.

\subsection{Key Concepts}

Define and explain the main concepts central to your research.

\subsection{Theoretical Models}

Discuss relevant theoretical models or frameworks that inform your work.

\section{Previous Research}

Review and analyze previous studies in your field.

\subsection{Seminal Works}

Discuss the foundational research that established the field. For example, cite important works like \cite{example2023}.

\subsection{Recent Developments}

Review recent advances and current trends in the research area \cite{example2024}.

\section{Research Gaps}

Identify gaps in the existing literature that your research aims to address.

\begin{itemize}
    \item Gap 1: [Describe the first identified gap]
    \item Gap 2: [Describe the second identified gap]
    \item Gap 3: [Describe the third identified gap]
\end{itemize}

\section{Summary}

Summarize the key points from the literature review and explain how your research will contribute to filling the identified gaps.

This review demonstrates that while significant progress has been made in [your field], there remain important questions that need to be addressed, particularly in the areas of [specific areas]. Your research aims to contribute to this knowledge by [your contribution].